### 2015-04-20 whoop.tex
updates

\subsubsection{Sound Partial Order Reduction}
\label{bf:reduction}

@@

Our approach to accelerating \corral is simple and yet effective: we simplify
the sequentialization that \corral performs by instrumenting \texttt{yield}
statements only at shared memory accesses that \whoop reported as potentially
racy. This effectively acts as a partial order reduction that can significantly
reduce the number of interleavings that \corral needs to explore, and thus
increase performance and scalability.

\ZRComment{Could this be cleaned up a bit? In particular, do we need to talk
about entry point pairs, or could we prove it just for any pair?}
We now show that our partial order reduction is sound: it does not miss any more
bugs than what \corral would miss even without taking advantage of the \whoop
race-related information. Let \corral run an $n$ amount of entry point pairs
with yields in all visible operations. Let this configuration be known as $C$.
Each entry point pair is running in a separate \corral process. \corral will
miss all bugs that are triggered by more than 3 bugs running concurrently and
all bugs that are triggered by investigating a larger than $r$ recursion bound
and larger than $k$ context switch bound. Let \corral then run the same $n$
amount of pairs, but this time with all \texttt{yield} statements in non-racy
shared memory accesses (according to \whoop) removed. Let this configuration be
known as $W+C$. Because these shared memory accesses cannot race, performing a
\texttt{yield} will not introduce any new program behaviors. Thus, \corral will
find the same bugs using the configuration $W+C$, as using the configuration
$C$.

\subsubsection{Granularity of Context-Switches}
\label{bf:granularity}

\ZRComment{I think this paragraph is not needed. You already talk about
how \corral by default instruments everything in the beginning of your previous
section. The command line switch /cooperative is I think an implementation
detail we do not have to mention. More generally, I would merge this
subsection with the previous one and I would keep the descriptions of
granularities.}
As aforementioned, \corral instruments by default a \texttt{yield} statement in
each visible operation. Using information from \whoop, though, we can avoid
instrumenting context-switches in memory accesses that do not race. To achieve
this, we use the \corral command line option \texttt{/cooperative}, which
disables \texttt{yield} instrumentation in \corral, and then we instrument
context-switches inside \whoop before sending these Boogie files to \corral. We
have implemented two different levels of context-switch instrumentation
granularity: \emph{\yieldcoarse} and \emph{\yieldmr}.

@@

We employ a simple, but effective, encoding of data-race checks within \corral.
For example, whenever there is a write access to a shared variable such as
\texttt{\$M.13 := 0}, we instrument the Boogie IVL code to check for write-write
races as follows:
%
\begin{boogie}
$M.13 := 0;        // original write
yield;             // allow for a context-switch
assert $M.13 == 0; // check written value
\end{boogie}
%
Likewise, for a read access to a shared variable such as \texttt{\$p0 :=
\$M.13}, we instrument the Boogie IVL code to check for read-write races as
follows:
\ZRComment{Why do you need this auxiliary variable?}
%
\begin{boogie}
$p0 := $M.13;       // original read
yield;              // allow for a context-switch
$rv0 := $M.13;      // $rv0 is auxiliary variable
assert $p0 == $rv0; // check read value
\end{boogie}

Note that our instrumentation conveniently tolerates most benign races, as it
does not report a write-write race if the two write accesses update the shared
memory location with the same value.  We introduce the instrumentation as a
precise feasibility check for the potential data races that \whoop reports.

>>>>

\subsubsection{Sound Partial-Order Reduction}
\label{bf:reduction}

@@

Our approach to accelerating \corral is simple and yet effective: we simplify
the sequentialization that \corral performs by instrumenting \texttt{yield}
statements only at shared memory accesses that \whoop reported as potentially
racy. This effectively acts as a partial-order reduction that can significantly
reduce the number of interleavings that \corral needs to explore, and thus
increase performance and scalability.

\ZRComment{Could this be cleaned up a bit? In particular, do we need to talk
about entry point pairs, or could we prove it just for any pair?}\PDComment{Lets also see what Ally thinks about this part.}
We now show that our partial-order reduction is sound: it does not miss any more
bugs than what \corral would miss even without taking advantage of the \whoop
race-related information. Let \corral run an $n$ amount of entry point pairs
with yields in all visible operations. Let this configuration be known as $C$.
Each entry point pair is running in a separate \corral process. \corral will
miss all bugs that are triggered by more than 3 bugs running concurrently and
all bugs that are triggered by investigating a larger than $r$ recursion bound
and larger than $k$ context switch bound. Let \corral then run the same $n$
amount of pairs, but this time with all \texttt{yield} statements in non-racy
shared memory accesses that are removed according to information from \whoop. Let this configuration be
known as $W+C$. Because these shared memory accesses cannot race, performing a
\texttt{yield} will not introduce any new program behaviors. Thus, \corral will
find the same bugs using the configuration $W+C$, as using the configuration
$C$.

We have implemented two different levels of context-switch instrumentation granularity:

@@

We employ a simple, but effective, encoding of data-race checks within \corral.
For example, whenever there is a write access to a shared variable, such as
\texttt{\$M.13 := 0}, we instrument the Boogie IVL code to check for write-write
races as follows:
%
\begin{boogie}
$M.13 := 0;        // original write
yield;             // allow for a context-switch
assert $M.13 == 0; // check written value
\end{boogie}
%
Likewise, for a read access to a shared variable, such as \texttt{\$p0 :=
\$M.13}, we instrument the Boogie IVL code to check for read-write races as
follows:
%
\begin{boogie}
$p0 := $M.13;        // original read
yield;               // allow for a context-switch
assert $p0 == $M.13; // check read value
\end{boogie}

Note that our instrumentation conveniently tolerates most benign races, as it does not report a write-write race if two write accesses update the same shared memory location with the same value.  We introduce the instrumentation as a precise feasibility check for the potential data races that \whoop reports.
